ASTR480 Final Report:\\ \textit{Asteroids in TESS}

### 2024-10-03 FinalReport/FinalReportDraft.tex
more slight changes to the start of the results section

This is the results for TESS sector 29.
This sector was chosen because it is early in the \qty{10}{\min} cadence of TESS FFIs, and had been fully run through TESSELLATE.
Similar results can be found in any of the sectors, just the computaion time was a limiting factor.

@@

The orbital element properties of the asteroids were returned by JPL Horizons queries.
A plot of the semi-major axis against the other orbital elements, eccentricity and inclination, is shown in \autoref{Fig:AEI}.
The disticntion between the resonances in the main belt are clearly seen. There are lines seperating the middle belt from the inner and outer belt.
The Jupiter trojans are well defined, at just past \qty{5}{\au}, with a small range of eccentricity but a large spread in the inclination.
Inbetween the outerbelt and the Jupiter trojans, sit some Mars crossers.
A some near earth objects (NEOs) at smaller $a$ and a few more objects that are scattered with high $e$ and or $i$ complete the distrabution.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{../OzData/AEIplot29.pdf}
  \caption[aei distribution]{a, e, i, plot of all the objects on sector 29}
  \label{Fig:AEI}
\end{figure}

The number the belong to each class of objects is highlighted in \autoref{Fig:NumPerClass}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{../OzData/classesBar29.pdf}
  \caption[Class distribution]{A distrabution of the number of asteroids per class that \texttt{SkyBot} knows the object is. }
  \label{Fig:NumPerClass}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{../OzData/recoverdHistBkgLimof10.pdf}
  \caption[Recovery plot]{A histogram of known average visual magnitude of each object against the whether or not the object has a lightcurve with an average flux value above 10 %!CHECK
    counts for its COM flux.
  }
  \label{Fig:RecovOverBkg}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{../OzData/pointsMatchesNumberHistTEST.pdf}
  \caption[short]{A histogram of the number of point in the lightcurve of each asteroid (blue) against the number of matches each asteroid gets in the \texttt{TESSELLATE} detections(orange dashed). }
  \label{Fig:MatchInterpHists}
\end{figure}

@@

>>>>

This is the results for TESS sector 29.
This sector was chosen because it is early in the \qty{10}{\min} cadence of TESS FFIs, and had been fully run through TESSELLATE.
Similar results can be found in any of the sectors, the computation time was a limiting factor in getting more sectors processed.

@@

The orbital element properties of the asteroids were returned by JPL Horizons queries.
A plot of the semi-major axis against the other orbital elements, eccentricity and inclination, is shown in \autoref{Fig:AEI}.
The distinction between the resonances in the main belt are clearly seen. There are lines separating the middle belt from the inner and outer belt.
The Jupiter Trojans are well-defined, at just past \qty{5}{\au}, with a small range of eccentricity but a large spread in the inclination.
In between the outer belt and the Jupiter Trojans, sit some Mars crossers.
A some near earth objects (NEOs) at smaller $a$ and a few more objects that are scattered with high $e$ and or $i$ complete the distribution.
These are all objects in the field of the instrument during the sector. 
Many of them will not be detected, as they will not be bright enough, this is seen below.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{../OzData/AEIplot29.pdf}
  \caption[aei distribution]{
    The $a$ against both $e$ and $i$ of all the objects that \texttt{SkyBot} found in Sector 29 with $V <\qty{20}{\mag}$. 
    (Other than the comets and centaurs with poorly defined $a$ values)
    The values of these proper elements were queried from JPL Horizons on 30/09/24.
  }
  \label{Fig:AEI}
\end{figure}

The number of asteroids belong to each class of objects is highlighted in \autoref{Fig:NumPerClass}. As expected from the orbital elements in \autoref{Fig:AEI}, the majority of the minor planets fall in the three regions of the main belt. \dots

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{../OzData/classesBar29.pdf}
  \caption[Class distribution]{A distribution of the number of asteroids per class that \texttt{SkyBot} found in the Sector. 
  As with \autoref{Fig:AEI}, this is for all objects brighter than \nth{20}\unit{\mag}
  For the class labels, MB is ``main belt'' and ``NEA'' is near earth asteroid.}
  \label{Fig:NumPerClass}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{../OzData/recoverdHistBkgLimof10.pdf}
  \caption[Recovery plot]{A histogram of known average visual magnitude of each object against the whether the object has a lightcurve with an average flux value above 10 %!CHECK
  counts for its COM flux.
  }
  \label{Fig:RecovOverBkg}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{../OzData/pointsMatchesNumberHistTEST.pdf}
  \caption[Number of observations or matches]{A histogram of the number of observations in the lightcurve of each asteroid (blue) against the number of matches each asteroid gets in the \texttt{TESSELLATE} detections(orange dashed). }
  \label{Fig:MatchInterpHists}
\end{figure}

\subsection{Period Analysis Results}\label{SubSec:PerRes}
